Arrows for Parallel Computations

### 2017-09-25 paper/content/motivation.tex
wip motivation

This is a big advantage as we do not introduce any new types as Monad solutions like the |Par| Monad do. We can just \enquote{plug} in parallel parts into sequential Arrow-based programs without having to change integral parts of the code.

@@

We evaluate the expressive power of arrow parallelism further by showing that it is possible to define algorithmic skeletons with Arrows (Sections \ref{sec:map-skeletons},~\ref{sec:topology-skeletons}).

Finally, we demonstrate that Arrow Parallelism is a viable alternative to existing approaches and prove that only low overhead is introduced, i.e. less than x\% \mbcomment{fix this after benchmarks are finally done} in Section \ref{sec:benchmarks}.

@@

\paragraph{Structure}
The remaining text is structures as follows. Section~\ref{sec:background} briefly introduces known parallel Haskell flavours (Sec.~\ref{sec:parEvalNIntro}) and gives an overview of Arrows to the reader (Sec.~\ref{sec:arrows}). Section~\ref{sec:related-work} discusses related work. Section~\ref{sec:parallel-arrows} defines Parallel Arrows and presents a basic interface. Section~\ref{futures} defines Futures for Parallel Arrows, this concept enables better communication. Section~\ref{sec:map-skeletons} presents some basic algorithmic skeletons  in our newly defined dialect: parallel |map| with and without load balancing. More advanced skeletons are showcased in Section~\ref{sec:topology-skeletons} (|pipe|, |ring|, |torus|). Section~\ref{sec:benchmarks} shows the benchmark results. Section~\ref{sec:conclusion} discusses future work and concludes.

>>>>

This is a big advantage as we do not introduce any new types as Monad solutions like the |Par| Monad do. We can just \enquote{plug} in parallel parts into sequential Arrow-based programs and libraries without having to change integral parts of the code. \mbcomment{mention Functions here? We have everything Eden has, but more.}

@@

We also show that it is possible to define algorithmic skeletons with Arrows (Sections \ref{sec:map-skeletons},~\ref{sec:topology-skeletons}) and finally demonstrate that Arrow Parallelism is a viable alternative to existing approaches and prove that only low overhead is introduced, i.e. less than x\% \mbcomment{fix this after benchmarks are finally done} as shown in Section \ref{sec:benchmarks}.

\mbcomment{Mention Future work here?}

@@

%\paragraph{Structure}
%The remaining text is structures as follows. Section~\ref{sec:background} briefly introduces known parallel Haskell flavours (Sec.~\ref{sec:parEvalNIntro}) and gives an overview of Arrows to the reader (Sec.~\ref{sec:arrows}). Section~\ref{sec:related-work} discusses related work. Section~\ref{sec:parallel-arrows} defines Parallel Arrows and presents a basic interface. Section~\ref{futures} defines Futures for Parallel Arrows, this concept enables better communication. Section~\ref{sec:map-skeletons} presents some basic algorithmic skeletons  in our newly defined dialect: parallel |map| with and without load balancing. More advanced skeletons are showcased in Section~\ref{sec:topology-skeletons} (|pipe|, |ring|, |torus|). Section~\ref{sec:benchmarks} shows the benchmark results. Section~\ref{sec:conclusion} discusses future work and concludes.
